\Rpackage{MSnbase}: labelled MS2 data pre-processing, visualisation and quantification.

### 2012-02-16 inst/doc/MSnbase-demo/MSnbase-demo.Rnw
typo in vignette
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@62736 bc3139a8-67e5-0310-9ffc-ced21a209358
is.na.MSnSet and vignette/doc updates
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@62825 bc3139a8-67e5-0310-9ffc-ced21a209358

<<removeNa,echo=TRUE>>=
sum(is.na(exprs(qnt)))
whichRow <- which(is.na(exprs(qnt))) %% nrow(qnt)
qnt <- qnt[-whichRow, ]
sum(is.na(exprs(qnt)))
@

@@

<<fdatanames, echo=TRUE, cache=FALSE>>=
all(fvarLabels(exp1) == fvarLabels(exp1))
fData(exp1)["BSA", 1:4]
fData(exp2)["BSA", 1:4]
@

>>>>

<<removeNa,echo=TRUE>>=
table(is.na(qnt))
whichRow <- which(is.na((qnt))) %% nrow(qnt)
qnt <- qnt[-whichRow, ]
sum(is.na(exprs(qnt)))
@

The \Rfunction{filterNA} method allows to filter features based on the proportion 
of missing data their carry, specified using the \Robject{pNA} argument. 
The same result as above could have been achieved with 
\Rfunction{qnt <- filterNA(qnt, pNA = 0)}, 
specifying that we allow 0 percent of missing data. 
See also the \Rfunction{plotNA} method to get an overview of the completeness 
of a data set.

@@

<<fdatanames, echo=TRUE, cache=FALSE>>=
stopifnot(all(fvarLabels(exp1) == fvarLabels(exp2)))
fData(exp1)["BSA", 1:4]
fData(exp2)["BSA", 1:4]
@
